Personalization and probabilities: impersonal propensities in online grocery shopping

### 2017-09-26 log.rmd
entered 22/34 page edits

## Thu 31 Aug 2017 16:34:43 BST
- long gap here -- due to important other activities such as summer holidays;  
- found the 1989 Humby article on demographics -- argues for the need to add lifestage to that of neighbourhood. 
- TODO: add reference to [@Humby_1989]

>>>>

## Thu 31 Aug 2017 16:34:43 BST
- long gap here -- due to important other activities such as summer holidays;  
- found the 1989 Humby article on demographics -- argues for the need to add lifestage to that of neighbourhood. 
- DONE: add reference to [@Humby_1989]
- reached conclusion in adding edits. Not sure if the section on Popper and possibiities trying to realize themselves is fleshed out enough.
- TODO: check if the last section does enough with propensities and the new features.

## Fri 08 Sep 2017 09:24:22 BST
- re-writing the conclusion today - did this on paper and now in file; it still needs more work
- but in order to do that, I've had to go back to beginning and go through the paper looking at the argument again.< 
- DONE: jump between D. and E. needs fixing. 
- DONE: section on list theory is still awkward -- Miller is fine, but what then?

## Tue 12 Sep 2017 14:29:19 CEST
- DONE: get Boltanski, 'finding ones ways in social space', 1983, has stuff on items and people; cf Distinction; added to ~/archive/boltanski_navigating_1983.pdf

## Mon 25 Sep 2017 09:37:00 BST
- started writing the revision letter and have detailed the main changes there: reply_to_reviews.md 
- redid the introduction again, take out lots of adjectives
- TODO: rewrite abstract and conclusion
- DONE: maybe should take out a lot of the list discussion. Is it too distracting?

## Tue 26 Sep 2017 09:13:38 BST
- realised I haven't actually entered the paper edits -- so going through the paper copy entering them. There are 34 pages -- do 15 today?  
- going through these edits, cutting out the list discussion as much as possible. In particular took out the more formal part of the list discussion -- not sure how it fits at all. 
- reached li 117/222, p18/34 today. 
- TODO: check list section again - does it flow?
- did some more -- p 22/34, li 153/222
